Periodograms for Multiband Astronomical Time Series

### 2015-05-12 writeup/paper.tex
add note about centering

\section{Standard Least Squares Spectral Fitting}
\sectlabel{standard_least_squares}
In this section we present a brief quantitative introduction to the least squares fitting formulation of the normalized periodogram of \eq{LombScargle}. We denote $N$ observed data points as
\begin{equation}
  D = \{t_k, y_k, \sigma_k\}_{k=1}^N
\end{equation}
where $t_k$ is the time of observation, $y_k$ is the observed value (typically a magnitude), and $\sigma_k$ describes the Gaussian errors on each value. \old{Without loss of generality} \new{For notational simplicity} we will assume that the data $y_k$ are centered such that the measurements within each band satisfy
\begin{equation}
  \eqlabel{ycentered}
  \frac{\sum_k w_ky_k}{\sum_k w_k} = 0
\end{equation}
where the weights are $w_k = \sigma_k^{-2}$.
\new{Though this assumption is important for the models presented in this section, it will become superfluous with the floating-mean models described in later sections.}

>>>>

\section{Standard Least Squares Spectral Fitting}
\sectlabel{standard_least_squares}
In this section we present a brief quantitative introduction to the least squares fitting formulation of the normalized periodogram of \eq{LombScargle}. We denote $N$ observed data points as
\begin{equation}
  D = \{t_k, y_k, \sigma_k\}_{k=1}^N
\end{equation}
where $t_k$ is the time of observation, $y_k$ is the observed value (typically a magnitude), and $\sigma_k$ describes the Gaussian errors on each value. \old{Without loss of generality} \new{For notational simplicity} we will assume \new{without loss of generality} that the data $y_k$ are centered such that the measurements within each band satisfy
\begin{equation}
  \eqlabel{ycentered}
  \frac{\sum_k w_ky_k}{\sum_k w_k} = 0
\end{equation}
where the weights are $w_k = \sigma_k^{-2}$.
\new{Though this assumption is essential to the models presented in this section, it will become superfluous with the floating-mean models described in later sections.}
